Output Summary

### 2021-06-21 03-post-process/output-plots.Rmd
Add summaries for AR(1) coefficients to output plots

    # give names
    dimnames(Ra) = dimnames(jags_data$p_remove)
    dimnames(Ma) = dimnames(jags_data$Mb_obs)

@@

>>>>

    # give names
    dimnames(Ra) = dimnames(jags_data$n_broodstock)
    dimnames(Ma) = dimnames(jags_data$Mb_obs)

@@

## AR(1) Coefficients

```{r}
post_summ(post, "kappa", Rhat = TRUE, neff = TRUE, digits = 3)
```

# JAGS Model and Data {.tabset .tabset-pills}

## JAGS Model Code

```{r, comment = NA}
# print the JAGS model code
cat(model_info$jags_model_code, sep = "\n")
```

## JAGS Model Data

```{r, comment = NA}
# print the JAGS model data
model_info$jags_data
```
